\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-08-08 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

\begin{thebibliography}{}
  \bibitem[Agarwal et al.(2019)]{AGARWAL2019715}
Agarwal, S., J. He, T. F. Sing, and C. Song. 2019. Do Real Estate Agents Have Information Advantages in Housing Markets? \textit{Journal of Financial Economics}, 134(3), 715-735.

\bibitem[Agarwal et al.(2024)]{AGARWAL2024103668}
Agarwal, S., Kuang, W., Wang, L., and Yang, Y. 2024. The role of agents in fraudulent activities: Evidence from the housing market in Beijing. \textit{Journal of Urban Economics}, 142, 103668.

\bibitem[Akerlof(1970)]{Akerlof_1970}
Akerlof, G. A. 1970. The Market for "Lemons": Quality Uncertainty and the Market Mechanism. \textit{The Quarterly Journal of Economics}, 84(3), 488-500.

\bibitem[Allen et al.(2023)]{RePEc:kap:jrefec:v:67:y:2023:i:3:d:10.1007_s11146-021-09858-w}
Allen, M. T., J. D. Benefield, and R. C. Rutherford. 2023. Co-Listing Strategies: Better Transaction Outcomes? \textit{The Journal of Real Estate Finance and Economics}, 67(3), 517-544.

\bibitem[Armstrong(2006)]{Armstrong2006}
Armstrong, M. 2006. Competition in Two-Sided Markets. \textit{The RAND Journal of Economics}, 37(3), 668-691.

\bibitem[Athey and Imbens(2006)]{https://doi.org/10.1111/j.1468-0262.2006.00668.x}
Athey, S., and G. W. Imbens. 2006. Identification and Inference in Nonlinear Difference-in-Differences Models. \textit{Econometrica}, 74(2), 431-497.% Available at \url{https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1468-0262.2006.00668.x}.

\bibitem[Athey and Imbens(2016)]{athey_recursive_2016}
Athey, S., and G. Imbens. 2016. Recursive Partitioning for Heterogeneous Causal Effects. \textit{Proceedings of the National Academy of Sciences of the United States of America}, 113(27), 7353-7360.

\bibitem[Azmi et al.(2012)]{AZMI2012406}
Azmi, D. I., H. A. Karim, and M. Z. M. Amin. 2012. Comparing the Walking Behaviour between Urban and Rural Residents. \textit{Procedia - Social and Behavioral Sciences}, 68(7), 406-416. % Available at \url{https://www.sciencedirect.com/science/article/pii/S1877042812057205}.

\bibitem[Bailey et al.(2018)]{bailey_economic_2018}
Bailey, M., R. Cao, T. Kuchler, and J. Stroebel. 2018. The Economic Effects of Social Networks: Evidence from the Housing Market. \textit{Journal of Political Economy}, 126(6), 2224-2276.

\bibitem[Barwick and Pathak(2015)]{https://doi.org/10.1111/1756-2171.12082}
Barwick, P. J., and P. A. Pathak. 2015. The Costs of Free Entry: An Empirical Study of Real Estate Agents in Greater Boston. \textit{The RAND Journal of Economics}, 46(1), 103-145.

\bibitem[Barwick et al.(2017)]{10.1257/app.20160214}
Barwick, P. J., P. A. Pathak, and M. Wong. 2017. Conflicts of Interest and Steering in Residential Brokerage. \textit{American Economic Journal: Applied Economics}, 9(3), 191-222.

\bibitem[Beck et al.(2022)]{doi:10.1080/10527001.2021.2016340}
Beck, J., F. Scott, and A. Yelowitz. 2022. The Impact of Real Estate Agent Specialization and Activity Level on Market Outcomes. \textit{Journal of Housing Research}, 31(2), 163-180.

\bibitem[Chen and Wen(2017)]{chen_great_2017}
Chen, K., and Y. Wen. 2017. The Great Housing Boom of China. \textit{American Economic Journal: Macroeconomics}, 9(2), 73-114.

\bibitem[Christensen and Timmins(2022)]{RePEc:ucp:jpolec:doi:10.1086/720140}
Christensen, P., and C. Timmins. 2022. Sorting or Steering: The Effects of Housing Discrimination on Neighborhood Choice. \textit{Journal of Political Economy}, 130(8), 2110-2163.

\bibitem[Chu et al.(2021)]{doi:10.1287/mnsc.2019.3550}
Chu, J., Y. Duan, X. Yang, and L. Wang. 2021. The Last Mile Matters: Impact of Dockless Bike Sharing on Subway Housing Price Premium. \textit{Management Science}, 67(1), 297-316.

\bibitem[d'Aspremont et al.(1979)]{daspremont_hotellings_1979}
d'Aspremont, C., J. J. Gabszewicz, and J.-F. Thisse. 1979. On Hotelling’s "Stability in Competition". \textit{Econometrica}, 47(5), 1145-1150.

\bibitem[Elvidge et al.(2021)]{elvidge_annual_2021}
Elvidge, C. D., M. Zhizhin, T. Ghosh, F.-C. Hsu, and J. Taneja. 2021. Annual Time Series of Global VIIRS Nighttime Lights Derived from Monthly Averages: 2012 to 2019. \textit{Remote Sensing}, 13(5), 922.

\bibitem[Farrell and Shapiro(1990)]{farrell_horizontal_1990}
Farrell, J., and C. Shapiro. 1990. Horizontal Mergers: An Equilibrium Analysis. \textit{American Economic Review}, 80(1), 107-126.

\bibitem[Genesove and Han(2012)]{GENESOVE201231}
Genesove, D., and L. Han. 2012. Search and Matching in the Housing Market. \textit{Journal of Urban Economics}, 72(1), 31-45.

\bibitem[Gilbukh and Goldsmith-Pinkham(2019)]{gilbukh_goldsmith-pinkham_2019}
Gilbukh, S., and P. Goldsmith-Pinkham. 2019. Heterogeneous Real Estate Agents and the Housing Cycle. Yale University Working Paper.

\bibitem[Glaeser et al.(2017)]{glaeser_real_2017}
Glaeser, E., W. Huang, Y. Ma, and A. Shleifer. 2017. A Real Estate Boom with Chinese Characteristics. \textit{Journal of Economic Perspectives}, 31(1), 93-116.

\bibitem[Grossman and Stiglitz(1980)]{grossman_impossibility_1980}
Grossman, S. J., and J. E. Stiglitz. 1980. On the Impossibility of Informationally Efficient Markets. \textit{American Economic Review}, 70(3), 393-408.

\bibitem[Han and Hong(2011)]{550a6ccf-cde2-3dd1-979f-1a8db2b8ceb9}
Han, L., and S.-H. Hong. 2011. Testing Cost Inefficiency Under Free Entry in the Real Estate Brokerage Industry. \textit{Journal of Business \& Economic Statistics}, 29(4), 564-578.

\bibitem[Han and Strange(2015)]{HAN2015813}
Han, L., and W. C. Strange. 2015. The Microstructure of Housing Markets: Search, Bargaining, and Brokerage. In \textit{Handbook of Regional and Urban Economics}, Vol. 5, pp. 813-886.

\bibitem[Handbury(2021)]{handbury_are_2021}
Handbury, J. 2021. Are Poor Cities Cheap for Everyone? Non-Homotheticity and the Cost of Living Across U.S. Cities. \textit{Econometrica}, 89(6), 2679-2715.

\bibitem[Hendel et al.(2009)]{hendel_relative_2009}
Hendel, I., A. Nevo, and F. Ortalo-Magné. 2009. The Relative Performance of Real Estate Marketing Platforms: MLS versus FSBOMadison.com. \textit{American Economic Review}, 99(5), 1878-1898.

\bibitem[Hong(2022)]{https://doi.org/10.1002/jae.2891}
Hong, S.-H. 2022. Real Estate Agents' Influence on Housing Search. \textit{Journal of Applied Econometrics}, 37(3), 563-582.

\bibitem[Hotelling(1929)]{hotelling_stability_1929}
Hotelling, H. 1929. The Stability in Competition. \textit{Economic Journal}, 39, 41-57.

\bibitem[Hsieh and Moretti(2003)]{hsieh_can_2003}
Hsieh, C.-T., and E. Moretti. 2003. Can Free Entry Be Inefficient? Fixed Commissions and Social Waste in the Real Estate Industry. \textit{Journal of Political Economy}, 111(5), 1076-1122.

\bibitem[Hui and Chan(2014)]{hui_foreign_2014}
Hui, E. C. M., and K. K. K. Chan. 2014. Foreign Direct Investment in China's real estate market. \textit{Habitat International}, 43, 231-239.

\bibitem[Jud et al.(1996)]{doi:10.1080/10835547.1996.12090852}
Jud, D., T. Seaks, and D. Winkler. 1996. Time on the Market: The Impact of Residential Brokerage. \textit{Journal of Real Estate Research}, 12(2), 447-458.

\bibitem[Langley and Leyshon(2017)]{Langley_Leyshon_2017}
Langley, P., and A. Leyshon. 2017. Platform Capitalism: The Intermediation and Capitalisation of Digital Economic Circulation. \textit{Finance and Society}, 3(1), 11-31.

\bibitem[Levitt and Syverson(2008)]{d082a2db-5cce-33f2-87c4-9cb020cc6666}
Levitt, S. D., and C. Syverson. 2008. Market Distortions When Agents Are Better Informed: The Value of Information in Real Estate Transactions. \textit{The Review of Economics and Statistics}, 90(4), 599-611.

\bibitem[Li and Qi(2022)]{10.1093/cje/beac054}
Li, Z., and H. Qi. 2022. Platform Power: Monopolisation and Financialisation in the Era of Big Tech. \textit{Cambridge Journal of Economics}, 46(6), 1289-1314.

\bibitem[Li et al.(2019)]{LI2019165}
Li, H., Y. D. Wei, Y. Wu, and G. Tian. 2019. Analyzing Housing Prices in Shanghai with Open Data: Amenity, Accessibility, and Urban Structure. \textit{Cities}, 91, 165-179.

\bibitem[Liu et al.(2023)]{liu2023chrono-urbanism}
Liu, D., M.-P. Kwan, L. Wang, Z. Kan, J. Wang, and J. Huang. 2023. Development of a Chrono-Urbanism Status Composite Index under the 5/10/15-Minute City Concept Using Social Media Big Data. \textit{Tijdschrift voor Economische en Sociale Geografie}, Early View. doi:10.1111/tesg.12613.

\bibitem[Machado and Santos Silva(2019)]{machado_quantiles_2019}
Machado, J. A. F., and J. M. C. Santos Silva. 2019. Quantiles via Moments. \textit{Journal of Econometrics}, 213(1), 145-173.

\bibitem[McCrary(2008)]{MCCRARY2008698}
McCrary, J. 2008. Manipulation of the Running Variable in the Regression Discontinuity Design: A Density Test. \textit{Journal of Econometrics}, 142(2), 698-714.

\bibitem[MOHURD(2018)]{GB50180-2018}
Ministry of Housing and Urban-Rural Development of China. 2018. \textit{Urban Residential Area Planning and Design Standard (GB50180-2018)}. Available from \url{http://www.moe.gov.cn/jyb_xwfb/xw_zt/moe_357/jyzt_2019n/2019_zt13/zcwj/201906/t20190606_384732.html}. (in Chinese).

\bibitem[Peng(2023)]{peng_mortgage_2023}
Peng, Y. 2023. Mortgage Credit and Housing Markets. \textit{SSRN Electronic Journal}, Working Paper. Available at \url{https://ssrn.com/abstract=4537500} or \url{http://dx.doi.org/10.2139/ssrn.4537500}.

\bibitem[Piazzesi et al.(2020)]{10.1257/aer.20141772}
Piazzesi, M., M. Schneider, and J. Stroebel. 2020. Segmented Housing Search. \textit{American Economic Review}, 110(3), 720-759.

\bibitem[Pope et al.(2015)]{POPE201589}
Pope, D. G., J. C. Pope, and J. R. Sydnor. 2015. Focal Points and Bargaining in Housing Markets. \textit{Games and Economic Behavior}, 93, 89-107.

\bibitem[Qu et al.(2021)]{qu_identifying_2021}
Qu, W., Y. Huang, and G. Deng. 2021. Identifying the Critical Factors Behind the Second-Hand Housing Price Concession: Empirical Evidence from China. \textit{Habitat International}, 117, 102442.

\bibitem[Rochet and Tirole(2003)]{10.1162/154247603322493212}
Rochet, J.-C., and J. Tirole. 2003. Platform Competition in Two-Sided Markets. \textit{Journal of the European Economic Association}, 1(4), 990-1029.

\bibitem[Rochet and Tirole(2006)]{https://doi.org/10.1111/j.1756-2171.2006.tb00036.x}
Rochet, J.-C., and J. Tirole. 2006. Two-Sided Markets: A Progress Report. \textit{The RAND Journal of Economics} 37(3): 645-667. % https://doi.org/10.1111/j.1756-2171.2006.tb00036.x.

\bibitem[Rosen(1974)]{Rosen_hedonic}
Rosen, S. 1974. Hedonic Prices and Implicit Markets: Product Differentiation in Pure Competition. \textit{Journal of Political Economy}, 82(1), 34-55.% Available at \url{http://www.jstor.org/stable/1830899}.

\bibitem[Rysman(2009)]{10.1257/jep.23.3.125}
Rysman, M. 2009. The Economics of Two-Sided Markets. \textit{Journal of Economic Perspectives} 23(3): 125-143. % https://doi.org/10.1257/jep.23.3.125.

\bibitem[Salz(2022)]{salz_intermediation_2022}
Salz, T. 2022. Intermediation and Competition in Search Markets: An Empirical Case Study. \textit{Journal of Political Economy}, 130(2), 310-345.

\bibitem[Sirmans et al.(1991)]{SIRMANS1991207}
Sirmans, C. F., G. K. Turnbull, and J. D. Benjamin. 1991. The Markets for Housing and Real Estate Broker Services. \textit{Journal of Housing Economics}, 1(3), 207-217.

\bibitem[Van Donkelaar et al.(2021)]{doi:10.1021/acs.est.1c05309}
Van Donkelaar, A., M. S. Hammer, L. Bindle, M. Brauer, J. R. Brook, M. J. Garay, N. C. Hsu, O. V. Kalashnikova, R. A. Kahn, C. Lee, R. C. Levy, A. Lyapustin, A. M. Sayer, and R. V. Martin. 2021. Monthly Global Estimates of Fine Particulate Matter and Their Uncertainty. \textit{Environmental Science \& Technology}, 55(22), 15287-15300.

\bibitem[Van Nieuwerburgh and Veldkamp(2010)]{NIEUWERBURGH_information}
Van Nieuwerburgh, S., and L. Veldkamp. 2010. Information Acquisition and Under-Diversification. \textit{The Review of Economic Studies}, 77(2), 779-805.

\bibitem[Varian(2014)]{10.1257/jep.28.2.3}
Varian, H. R. 2014. Big Data: New Tricks for Econometrics. \textit{Journal of Economic Perspectives}, 28(2), 3-28.

\bibitem[Wei and Zhang(2011)]{wei_competitive_2011}
Wei, S.-J., and X. Zhang. 2011. The Competitive Saving Motive: Evidence from Rising Sex Ratios and Savings Rates in China. \textit{Journal of Political Economy}, 119(3), 511-564.

\bibitem[Weyl(2010)]{10.1257/aer.100.4.1642}
Weyl, E. G. 2010. A Price Theory of Multi-Sided Platforms. \textit{American Economic Review} 100(4): 1642-1672. % https://doi.org/10.1257/aer.100.4.1642.

\bibitem[Williams(1998)]{williams_agency_1998}
Williams, J. T. 1998. Agency and Brokerage of Real Assets in Competitive Equilibrium. \textit{Review of Financial Studies}, 11(2), 239-280.

\bibitem[Wong et al.(2012)]{wong_liquidity_2012}
Wong, S. K., C. Y. Yiu, and K. W. Chau. 2012. Liquidity and Information Asymmetry in the Real Estate Market. \textit{The Journal of Real Estate Finance and Economics}, 45(1), 49-62.

\bibitem[Yang et al.(2021)]{YANG2021102359}
Yang, L., K. W. Chau, and Y. Chen. 2021. Impacts of Information Asymmetry and Policy Shock on Rental and Vacancy Dynamics in Retail Property Markets. \textit{Habitat International}, 111, 102359.

\bibitem[Zhang et al.(2021)]{ZHANG2021101104}
Zhang, X., Z. Lin, Y. Zhang, Y. Zheng, and J. Zhang. 2021. Online Property Brokerage Platform and Prices of Second-Hand Houses: Evidence from Lianjia's Entry. \textit{Electronic Commerce Research and Applications}, 50, 101104.

\bibitem[Zhao et al.(2017)]{zhao_forecasting_2017}
Zhao, N., Y. Liu, G. Cao, E. L. Samson, and J. Zhang. 2017. Forecasting China's GDP at the Pixel Level Using Nighttime Lights Time Series and Population Images. \textit{GIScience \& Remote Sensing}, 54(3), 407-425.

\bibitem[Zhao(2015)]{zhao_rational_2015}
Zhao, B. 2015. Rational Housing Bubble. \textit{Economic Theory}, 60(1), 141-201.

\bibitem[Zhu and Iansiti(2019)]{WOS:000454186600016}
Zhu, F., and M. Iansiti. 2019. Why Some Platforms Thrive and Others Don't. \textit{Harvard Business Review}, 97(1), 118-125.

\bibitem[Zumpano et al.(2003)]{ZUMPANO2003134}
Zumpano, L. V., K. H. Johnson, and R. I. Anderson. 2003. Internet Use and Real Estate Brokerage Market Intermediation. \textit{Journal of Housing Economics}, 12(2), 134-150.

>>>>

\begin{thebibliography}{}
  \bibitem[Agarwal et al.(2019)]{AGARWAL2019715}
Agarwal S, He J, Sing TF, Song C (2019) Do real estate agents have information advantages in housing markets? \textit{Journal of Financial Economics} 134(3):715-735.

\bibitem[Agarwal et al.(2024)]{AGARWAL2024103668}
Agarwal S, Kuang W, Wang L, Yang Y (2024) The role of agents in fraudulent activities: Evidence from the housing market in Beijing. \textit{Journal of Urban Economics} 142:103668.

\bibitem[Akerlof(1970)]{Akerlof_1970}
Akerlof GA (1970) The Market for “Lemons”: Quality Uncertainty and the Market Mechanism. \textit{The Quarterly Journal of Economics} 84(3):488.

\bibitem[Allen et al.(2023)]{RePEc:kap:jrefec:v:67:y:2023:i:3:d:10.1007_s11146-021-09858-w}
Allen MT, Benefield JD, Rutherford RC (2023) Co-Listing Strategies: Better Transaction Outcomes? \textit{The Journal of Real Estate Finance and Economics} 67(3):517-544.

\bibitem[Armstrong(2006)]{Armstrong2006}
Armstrong M (2006) Competition in two-sided markets. \textit{The RAND Journal of Economics} 37(3):668-691.

\bibitem[Athey and Imbens(2006)]{https://doi.org/10.1111/j.1468-0262.2006.00668.x}
Athey S, Imbens GW (2006) Identification and Inference in Nonlinear Difference-in-Differences Models. \textit{Econometrica} 74(2):431-497.

\bibitem[Athey and Imbens(2016)]{athey_recursive_2016}
Athey S, Imbens GW (2016) Recursive partitioning for heterogeneous causal effects. \textit{Proceedings of the National Academy of Sciences} 113(27):7353-7360.

\bibitem[Azmi et al.(2012)]{AZMI2012406}
Azmi DI, Karim HA, Amin MZM (2012) Comparing the Walking Behaviour between Urban and Rural Residents. \textit{Procedia - Social and Behavioral Sciences} 68:406-416.

\bibitem[Bailey et al.(2018)]{bailey_economic_2018}
Bailey M, Cao R, Kuchler T, Stroebel J (2018) The Economic Effects of Social Networks: Evidence from the Housing Market. \textit{Journal of Political Economy} 126(6):2224-2276.

\bibitem[Barwick and Pathak(2015)]{https://doi.org/10.1111/1756-2171.12082}
Barwick PJ, Pathak PA (2015) The costs of free entry: an empirical study of real estate agents in Greater Boston. \textit{The RAND Journal of Economics} 46(1):103-145.

\bibitem[Barwick et al.(2017)]{10.1257/app.20160214}
Barwick PJ, Pathak PA, Wong M (2017) Conflicts of Interest and Steering in Residential Brokerage. \textit{American Economic Journal Applied Economics} 9(3):191-222.

\bibitem[Beck et al.(2022)]{doi:10.1080/10527001.2021.2016340}
Beck J, Scott F, Yelowitz A (2022) The Impact of Real Estate Agent Specialization and Activity Level on Market Outcomes. \textit{Journal of Housing Research} 31(2):163-180.

\bibitem[Chen and Wen(2017)]{chen_great_2017}
Chen K, Wen Y (2017) The Great Housing Boom of China. \textit{American Economic Journal Macroeconomics} 9(2):73-114.

\bibitem[Christensen and Timmins(2022)]{RePEc:ucp:jpolec:doi:10.1086/720140}
Christensen P, Timmins C (2022) Sorting or Steering: The Effects of Housing Discrimination on Neighborhood Choice. \textit{Journal of Political Economy} 130(8):2110-2163.

\bibitem[Chu et al.(2021)]{doi:10.1287/mnsc.2019.3550}
Chu J, Duan Y, Yang X, Wang L (2021) The Last Mile Matters: Impact of Dockless Bike Sharing on Subway Housing Price Premium. \textit{Management Science} 67(1):297-316.

\bibitem[d'Aspremont et al.(1979)]{daspremont_hotellings_1979}
D'Aspremont C, Gabszewicz JJ, Thisse J f. (1979) On Hotelling's “Stability in Competition.” \textit{Econometrica} 47(5):1145-1150.

\bibitem[Elvidge et al.(2021)]{elvidge_annual_2021}
Elvidge CD, Zhizhin M, Ghosh T, Hsu FC, Taneja J (2021) Annual Time Series of Global VIIRS Nighttime Lights Derived from Monthly Averages: 2012 to 2019. \textit{Remote Sensing} 13(5):922.

\bibitem[Farrell and Shapiro(1990)]{farrell_horizontal_1990}
Farrell J, Shapiro C (1990) Horizontal Mergers: An Equilibrium Analysis. \textit{American Economic Review} 80(1):107-126.

\bibitem[Genesove and Han(2012)]{GENESOVE201231}
Genesove D, Han L (2012) Search and matching in the housing market. \textit{Journal of Urban Economics} 72(1):31-45.

\bibitem[Gilbukh and Goldsmith-Pinkham(2019)]{gilbukh_goldsmith-pinkham_2019}
Gilbukh S, Goldsmith-Pinkham P (2019) Heterogeneous Real Estate Agents and the Housing Cycle. \textit{SSRN Electronic Journal}.

\bibitem[Glaeser et al.(2017)]{glaeser_real_2017}
Glaeser E, Huang W, Ma Y, Shleifer A (2017) A Real Estate Boom with Chinese Characteristics. \textit{The Journal of Economic Perspectives} 31(1):93-116.

\bibitem[Grossman and Stiglitz(1980)]{grossman_impossibility_1980}
Grossman SJ, Stiglitz JE (1980) On the impossibility of informationally efficient markets. \textit{American Economic Review} 70(3):393-408.

\bibitem[Han and Hong(2011)]{550a6ccf-cde2-3dd1-979f-1a8db2b8ceb9}
Han L, Hong SH (2011) Testing Cost Inefficiency Under Free Entry in the Real Estate Brokerage Industry. \textit{Journal of Business \& Economic Statistics} 29(4):564-578.

\bibitem[Han and Strange(2015)]{HAN2015813}
Han L, Strange WC (2015) The Microstructure of Housing Markets. \textit{Handbook of Regional and Urban Economics}. 813-886.

\bibitem[Handbury(2021)]{handbury_are_2021}
Handbury J (2021) Are Poor Cities Cheap for Everyone? Non-Homotheticity and the Cost of Living Across U.S. Cities. \textit{Econometrica} 89(6):2679-2715.

\bibitem[Hendel et al.(2009)]{hendel_relative_2009} 
Hendel I, Nevo A, Ortalo-Magné F (2009) The Relative Performance of Real Estate Marketing Platforms: MLS versus FSBOMadison.com. \textit{American Economic Review} 99(5):1878-1898.

\bibitem[Hong(2022)]{https://doi.org/10.1002/jae.2891}
Hong S-H (2022) Real estate agents' influence on housing search. \textit{Journal of Applied Econometrics} 37(3):563-582.

\bibitem[Hotelling(1929)]{hotelling_stability_1929}
Hotelling H (1929) Stability in Competition. \textit{The Economic Journal} 39(153):41-57.

\bibitem[Hsieh and Moretti(2003)]{hsieh_can_2003}
Hsieh C-T, Moretti E (2003) Can Free Entry Be Inefficient? Fixed Commissions and Social Waste in the Real Estate Industry. \textit{Journal of Political Economy} 111(5):1076-1122.

\bibitem[Hui and Chan(2014)]{hui_foreign_2014}
Hui ECM, Chan KKK (2014) Foreign direct investment in China's real estate market. \textit{Habitat International} 43:231-239.

\bibitem[Jud et al.(1996)]{doi:10.1080/10835547.1996.12090852}
Jud D, Seaks T, Winkler D (1996) Time on the Market: The Impact of Residential Brokerage. \textit{Journal of Real Estate Research} 12(2):447-458.

\bibitem[Langley and Leyshon(2017)]{Langley_Leyshon_2017}
Langley P, Leyshon A (2017) Platform capitalism: The intermediation and capitalisation of digital economic circulation. \textit{Finance and Society} 3(1):11-31.

\bibitem[Levitt and Syverson(2008)]{d082a2db-5cce-33f2-87c4-9cb020cc6666}
Levitt SD, Syverson C (2008) Market Distortions When Agents Are Better Informed: The Value of Information in Real Estate Transactions. \textit{The Review of Economics and Statistics} 90(4):599-611.

\bibitem[Li et al.(2019)]{LI2019165}
Li H, Wei YD, Wu Y, Tian G (2019) Analyzing housing prices in Shanghai with open data: Amenity, accessibility and urban structure. \textit{Cities} 91:165-179.

\bibitem[Li and Qi(2022)]{10.1093/cje/beac054}
Li Z, Qi H (2022) Platform power: monopolisation and financialisation in the era of big tech. \textit{Cambridge Journal of Economics} 46(6):1289-1314.

\bibitem[Liu et al.(2023)]{liu2023chrono-urbanism}
Liu D, Kwan M-P, Wang L, Kan Z, Wang J, Huang J (2024) Development of a Chrono-Urbanism Status Composite Index under the 5/10/15-Minute City Concept Using Social Media Big Data. \textit{Tijdschrift Voor Economische En Sociale Geografie}.

\bibitem[Machado and Santos Silva(2019)]{machado_quantiles_2019}
Machado JAF, Silva JMCS (2019) Quantiles via moments. \textit{Journal of Econometrics} 213(1):145-173.

\bibitem[McCrary(2008)]{MCCRARY2008698}
McCrary J (2008) Manipulation of the running variable in the regression discontinuity design: A density test. \textit{Journal of Econometrics} 142(2):698-714.

\bibitem[MOHURD(2018)]{GB50180-2018}
Ministry of Housing and Urban-Rural Development of China. 2018. Urban residential area planning and design standard (GB50180-2018). Available at: \url{http://www.moe.gov.cn/jyb_xwfb/xw_zt/moe_357/jyzt_2019n/2019_zt13/zcwj/201906/t20190606_384732.html} (accessed July 7, 2023). (in Chinese).

\bibitem[Peng(2023)]{peng_mortgage_2023}
Peng Y (2023) Mortgage Credit and Housing Markets. \textit{SSRN Electronic Journal}. % Available at \url{https://ssrn.com/abstract=4537500} or \url{http://dx.doi.org/10.2139/ssrn.4537500}.

\bibitem[Piazzesi et al.(2020)]{10.1257/aer.20141772}
Piazzesi M, Schneider M, Stroebel J (2020) Segmented Housing Search. \textit{American Economic Review} 110(3):720-759.

\bibitem[Pope et al.(2015)]{POPE201589}
Pope DG, Pope JC, Sydnor JR (2015) Focal points and bargaining in housing markets. \textit{Games and Economic Behavior} 93:89-107.

\bibitem[Qu et al.(2021)]{qu_identifying_2021}
Qu W, Huang Y, Deng G (2021) Identifying the critical factors behind the second-hand housing price concession: Empirical evidence from China. \textit{Habitat International} 117:102442.

\bibitem[Rochet and Tirole(2003)]{10.1162/154247603322493212}
Rochet JC, Tirole J (2003) Platform Competition in Two-Sided Markets. \textit{Journal of the European Economic Association} 1(4):990-1029.

\bibitem[Rochet and Tirole(2006)]{https://doi.org/10.1111/j.1756-2171.2006.tb00036.x}
Rochet JC, Tirole J (2006) Two-sided markets: a progress report. \textit{The RAND Journal of Economics} 37(3):645-667.

\bibitem[Rosen(1974)]{Rosen_hedonic}
Rosen S (1974) Hedonic Prices and Implicit Markets: Product Differentiation in Pure Competition. \textit{Journal of Political Economy} 82(1):34-55.

\bibitem[Rysman(2009)]{10.1257/jep.23.3.125}
Rysman M (2009) The Economics of Two-Sided Markets. \textit{Journal of Economic Perspectives} 23(3):125-143.

\bibitem[Salz(2022)]{salz_intermediation_2022}
Salz T (2022) Intermediation and Competition in Search Markets: An Empirical Case Study. \textit{Journal of Political Economy} 130(2):310-345.

\bibitem[Sirmans et al.(1991)]{SIRMANS1991207}
Sirmans CF, Turnbull GK, Benjamin JD (1991) The markets for housing and real estate broker services. \textit{Journal of Housing Economics} 1(3):207-217.

\bibitem[Van Donkelaar et al.(2021)]{doi:10.1021/acs.est.1c05309}
Van Donkelaar A, Hammer MS, Bindle L, Brauer M, Brook JR, Garay MJ, Hsu NC, et al. (2021) Monthly Global Estimates of Fine Particulate Matter and Their Uncertainty. \textit{Environmental Science \& Technology} 55(22):15287-15300.

\bibitem[Van Nieuwerburgh and Veldkamp(2010)]{NIEUWERBURGH_information}
Van Nieuwerburgh S, Veldkamp L (2010) Information Acquisition and Under-Diversification. \textit{The Review of Economic Studies} 77(2):779-805.

\bibitem[Varian(2014)]{10.1257/jep.28.2.3}
Varian HR (2014) Big Data: New Tricks for Econometrics. \textit{Journal of Economic Perspectives} 28(2):3-28.

\bibitem[Wei and Zhang(2011)]{wei_competitive_2011}
Wei SJ, Zhang X (2011) The Competitive Saving Motive: Evidence from Rising Sex Ratios and Savings Rates in China. \textit{Journal of Political Economy} 119(3):511-564.

\bibitem[Weyl(2010)]{10.1257/aer.100.4.1642}
Weyl EG (2010) A Price Theory of Multi-Sided Platforms. \textit{American Economic Review} 100(4):1642-1672.

\bibitem[Williams(1998)]{williams_agency_1998}
Williams JT (1998) Agency and Brokerage of Real Assets in Competitive Equilibrium. \textit{Review of Financial Studies} 11(2):239-280.

\bibitem[Wong et al.(2012)]{wong_liquidity_2012}
Wong SK, Yiu CY, Chau KW (2011) Liquidity and Information Asymmetry in the Real Estate Market. \textit{The Journal of Real Estate Finance and Economics} 45(1):49-62.

\bibitem[Yang et al.(2021)]{YANG2021102359}
Yang L, Chau KW, Chen Y (2021) Impacts of information asymmetry and policy shock on rental and vacancy dynamics in retail property markets. \textit{Habitat International} 111:102359.

\bibitem[Zhang et al.(2021)]{ZHANG2021101104}
Zhang X, Lin Z, Zhang Y, Zheng Y, Zhang J (2021) Online property brokerage platform and prices of second-hand houses: Evidence from Lianjia's entry. \textit{Electronic Commerce Research and Applications} 50:101104.

\bibitem[Zhao(2015)]{zhao_rational_2015}
Zhao B (2015) Rational housing bubble. \textit{Economic Theory} 60(1):141-201.

\bibitem[Zhao et al.(2017)]{zhao_forecasting_2017}
Zhao N, Liu Y, Cao G, Samson EL, Zhang J (2017) Forecasting China's GDP at the pixel level using nighttime lights time series and population images. \textit{GIScience \& Remote Sensing} 54(3):407-425.

\bibitem[Zhu and Iansiti(2019)]{WOS:000454186600016}
Zhu F, Iansiti M (2019) Why Some Platforms Thrive and Others Don't. \textit{Harvard Business Review} 97(1):118-125.

\bibitem[Zumpano et al.(2003)]{ZUMPANO2003134}
Zumpano LV, Johnson KH, Anderson RI (2003) Internet use and real estate brokerage market intermediation. \textit{Journal of Housing Economics} 12(2):134-150.
